---
title: "Academic paths"
author: "Cécile Armand"
date: "`r lubridate::today()`"

output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    number_sections: false
    code_folding: show # hide
    fig_caption: true
    df_print: paged

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(networkD3)
library(htmlwidgets)
```

# From list to sequences

We start from the "aucplaces" dataset which contains several useful synthetic variables 
  * the total number of degree obtained
  * the highest degree obtained
  * the main field of study (corresponding to the most specialized or highest degree obtaied)

Load packages
```{r}
library(tidyverse)
library(networkD3)
library(htmlwidgets)
```


Load data
```{r}
library(readr)
aucplaces <- read_csv("~/Places AUC/aucplaces.csv")
aucplaces
```
<br>
Workflow
  1. Remove honorary degrees
  2. Filter students with more than one degree
  3. Identify duplicated years (simultaneous degrees)
  4. Rank universities by order of succession 

(1) Remove honorary degrees
```{r}
aucplaces %>% group_by(Honorary) %>% count() # 8 honorary degrees
auc_rank <- aucplaces %>% filter(is.na(Honorary)) # 674 degrees remained
```
<br>
(2) Filter students with more than one degree
```{r}
auc_rank <- auc_rank %>% group_by(Name_eng) %>% add_tally()
auc_rank <- auc_rank %>% filter(n>1) # 452 curricula remain
auc_rank <- auc_rank %>% filter(!Name_eng %in% c("Fan_Robert", "Lee_Poy Gum")) # obtained only 1 degree (false duplicate)
auc_rank %>% group_by(Name_eng) %>% count() # 195 unique individuals earned at least 2 degrees (up to 5)
```
<br>
(3) Identify duplicated years (simultaneous degrees) 
```{r}
# 35 individuals earned 2 or more (up to 4) degrees the same year 
multiple_rank <- auc_rank %>% group_by(Name_eng, Year_start) %>% count()
multiple_rank_2  <- multiple_rank %>% filter(n>1)
```
<br>
(4) Rank university by order of succession
```{r}
# filter out multiple rank  
auc_rank_filtered <- auc_rank %>% filter(!Name_eng %in% multiple_rank_2$Name_eng)
auc_rank_filtered %>% group_by(Name_eng, Year_start) %>% count(sort = TRUE)
# rank degrees 
auc_rank_filtered <- auc_rank_filtered %>% mutate(rank = rank(Year_start)) %>% 
  relocate(rank, .before = "Year_start")
```
<br>
Export the dataset "auc_rank" to solve conflicts 
```{r}
write.csv(auc_rank, "auc_rank.csv")
```
<br>
Reimport the manually curated dataset 
```{r}
library(readr)
auc_rank_solved <- read_csv("~/Places AUC/Sequence/auc_rank_solved.csv")
auc_rank_solved
```
<br>
Bind with filtered data
```{r}
auc_rank_all <- bind_rows(auc_rank_filtered, auc_rank_solved) # 811 degrees 
auc_rank_all %>% group_by(Name_eng) %>% count(sort = TRUE) # 362 individuals, from 2 to 6 degrees
auc_rank_all
```
<br>
We can already use this to analyze the first/last universities attended. 

Pivot wider to visualize the sequence of universities and/or disciplines, etc:
```{r}
auc_rank_to_pivot <- auc_rank_all %>% select(Name_eng, University, rank) 
auc_rank_pivot <- auc_rank_to_pivot %>%
  pivot_wider(names_from = rank, names_glue = "{.value}_{rank}", values_from = University)
auc_sequence <- auc_rank_pivot %>% relocate("University_1", .before = "University_2") %>%
  mutate_all(as.character)
auc_sequence %>% arrange(University_1, University_2)
```
<br>
Join with place number, period and main field 
```{r}

library(readr)
places_attributes <- read_csv("~/Places AUC/places_attributes.csv")

auc_attrib <- aucplaces %>% select(Name_eng, Name_zh, Field_high, period) %>% unique()
place_attrib <- places_attributes %>% select(Name_eng, PlaceLabel)  %>% unique()

auc_sequence <- left_join(auc_sequence, auc_attrib)
auc_sequence <- left_join(auc_sequence, place_attrib)

auc_sequence_df <- auc_sequence %>%
  mutate_all(as.character)
```
<br>
Export for further cleaning
```{r}
write.csv(auc_sequence_df, "auc_sequence_df.csv")
```
<br>
Re-import clean dataset
```{r}
auc_sequence_clean <- read_csv("~/Places AUC/Sequence/auc_sequence_clean.csv")
```
<br> 
Join with employment data 
```{r}
auc_job <- aucplaces %>% select(Name_eng, Employer_main, Sector_1, Sector_2, start, end) %>% distinct()
auc_sequence_job <- left_join(auc_sequence_clean, auc_job)
auc_sequence_job
```

# From sequences to paths

Select two first degrees
```{r}
# two first degrees 
auc_seq_2 <- auc_sequence_job  %>% select('1', '2') %>%
  rename(source = '1', target = '2')
```
<br>
Remove missing values and compute link weight 
```{r}
links <- auc_seq_2 %>%
  group_by(source, target) %>% 
  drop_na(target)  %>% 
  count() %>% 
  rename(value = "n")

links %>% arrange(desc(value))

```
<br> 
Export table of links 
```{r}
write.csv(links, "deg-1-2.csv")
```
<br>
Focus on migrations (remove students who stayed in the same college)
```{r}
link <- links[links$source != links$target, ]
```
<br>
Focus on most important flows (n>1) 
```{r}
link <- link %>% filter(value>1)
```
<br>
Create nodes 
```{r}
node <- data.frame(
  name=c(as.character(link$source), 
         as.character(link$target)) %>% unique()
)
```
<br>
Create unique id for each connection
```{r}
link$IDsource <- match(link$source, node$name)-1 
link$IDtarget <- match(link$target, node$name)-1
```
<br>
Build the networks
```{r}
p <- sankeyNetwork(Links = link, Nodes = node,
                    Source = "IDsource", Target = "IDtarget",
                    Value = "value", NodeID = "name", 
                    sinksRight=FALSE)
p
```
<br>
Save the widget
```{r}
library(htmlwidgets)
saveWidget(p, file=paste0( getwd(), "/deg1-2.html"))
```
<br>
We can apply the same code for the next degrees (2 to 3, 3 to 4...) for the students who attended more than 2 universities.

# From college to work


First identify and remove students/colleges duplicates

```{r}
auc_pair <- aucplaces %>% select(Name_eng, University, Employer_main, Sector_1, Sector_2) %>% unique()
```
<br>
Join with places number
```{r}
auc_pair <- left_join(place_attrib, auc_pair)
auc_pair
```
<br>
Select university and employer to create a list of links
```{r}
university_employer <- auc_pair %>% select(University, Employer_main)
```
<br>
Create and save list of links
```{r}
links <- university_employer %>%
  rename(source = University, target = Employer_main) %>%
  group_by(source, target) %>% 
  drop_na(target) %>% 
  count() %>% 
  rename(value = "n")

links %>% arrange(desc(value))

write.csv(links, "univ_employer.csv")
```
<br>
Focus on the most important employers
```{r}
link <- links %>% filter(value>1)
```
<br>
Create node list (contains every entity involved in the flow)
```{r}
node <- data.frame(
  name=c(as.character(link$source), 
         as.character(link$target)) %>% unique()
)
```
<br>
Create unique id for each connection
```{r}
link$IDsource <- match(link$source, node$name)-1 
link$IDtarget <- match(link$target, node$name)-1
```
<br>
Build the network
```{r}
p <- sankeyNetwork(Links = link, Nodes = node,
                    Source = "IDsource", Target = "IDtarget",
                    Value = "value", NodeID = "name", 
                    sinksRight=FALSE)
p
```
<br>
Save the widget
```{r}
library(htmlwidgets)
saveWidget(p, file=paste0( getwd(), "/employer.html"))
```



